Togglge Smell Detection in Google Chrome

### 2015-12-07 paper/paper.tex
writing intro, adding figure

>>>>

They use feature toggle to manage the features during development as well as 
in testing and canary phase.

Chrome is a popular, large open source project that has been using feature toggles for more than five years and that we use as case study in this paper. 
Instead of having a single configuration file for toggles, Chrome has 
multiple “switch files” representing toggleable sets of related features. 
In Fig~\ref{fig:switch-sets} we can see few of the switch-set files 
in Chrome containing toggles for their respective modules. 
We can see switch files for features related to how content is 
displayed in Chrome (content\_switches.cc) or to testing of GPU 
(test\_switches.cc).
\begin{figure}
\includegraphics[height=0.5in,width=3.5in]{figure/switches.png}
\caption{Toggle set / Switch set files in Chrome source code.}
\label{fig:switch-sets}
\end{figure}
Each switch file contains a set of feature toggles that can
be enabled or disabled. In Chrome, feature toggles are strings
that can be set or unset. For example, Fig.~\ref{fig:content-toggles} 
shows that the
feature toggle kDisableFlashFullscreen3d is being set by
giving it the value “disable-flash-fullscreen-3d”. This disables
the feature that renders graphics in 3D when flash content is
presented full-screen. Advanced users might use this toggle
to improve performance~\cite{kDisableFlashFullscreen3d}.\\
\begin{figure}
\includegraphics[height=0.5in,width=3.5in]{figure/toggleassigned.png}
\caption{Example toggles inside content\_switches.cc}
\label{fig:content-toggles}
\end{figure}

While developers are working on a feature, 
toggles are used in an if condition to let this feature
turn on/off. In Google Chrome this is done by adding a toggle 
or removing it from the switch set or feature set file. 
For the above example of kDisableFlashFullscreen3d, 
Fig.~\ref{fig:toggle-use} is showing us that the feature toggle is 
being used in an if statement and if it is set it will not allow the 
rest of the code in the function to be executed, which enables 3D 
flash-fullscreen. That means the feature 3D flash-fullscreen has been 
disabled by turning this toggle on.\\
\begin{figure}
\includegraphics[height=2in,width=3.5in]{figure/toggle-use.png}
\caption{Example of use of toggle}
\label{fig:toggle-use}
\end{figure}
